Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2018-06-21 abstract.tex
Shorten abstract, neuro example.

\begin{abstract}
Across almost all scientific disciplines, instruments and methods for recording, storing and analyzing data are rapidly increasing in complexity.
Numerous data science tools are in development that aim to manage this complexity through development of open, reproducible workflows and the exchange of ideas across disciplines.
Successful navigation of this new data science landscape requires training in new programming languages and frameworks, as well as immersion in new modes of interaction that foster data sharing and collaborative software development. 
Unfortunately, learning these skills from traditional university curricula can be challenging because most courses are not designed to evolve on time scales that can keep pace with rapidly shifting data science methods.
Here we present the concept of a hack week as a novel and effective model offering opportunitites for networking and community building, education in state-of-the-art data science methods and immersion in collaborative project work.
We find that hack weeks are successful at cultivating collaboration and facilitating the exchange of knowledge.
Participants self-report that these events help them both in their day-to-day research as well as their careers.
Based on our results, we conclude that hack weeks present an effective, easy-to-implement, fairly low-cost tool to positively impact data analysis literacy in academic disciplines, foster collaboration and cultivate best practices.
\end{abstract}

>>>>

\begin{abstract}
Across many scientific disciplines, methods for recording, storing and analyzing data are rapidly increasing in complexity.
Facility in data science tools to manage this complexity requires training in new programming languages and frameworks, as well as immersion in new modes of interaction that foster data sharing and collaborative software development and exchange across disciplines.
Learning these skills from traditional university curricula can be challenging because most courses are not designed to evolve on time scales that can keep pace with rapidly shifting data science methods.
Here we present the concept of a hack week as a novel and effective model offering opportunitites for networking and community building, education in state-of-the-art data science methods and immersion in collaborative project work.
We find that hack weeks are successful at cultivating collaboration and facilitating the exchange of knowledge.
Participants self-report that these events help them both in their day-to-day research as well as their careers.
Based on our results, we conclude that hack weeks present an effective, easy-to-implement, fairly low-cost tool to positively impact data analysis literacy in academic disciplines, foster collaboration and cultivate best practices.
\end{abstract}

### 2018-06-21 results.tex
Shorten abstract, neuro example.

\subsection*{Examples of Hack Week Outcomes}
\label{sec:outcomes}
\subsubsection*{Example 1: Astro Hack Week}
In 2015, a small team used AHW to found a new software project called Stingray\footnote{https://github.com/StingraySoftware/stingray} with the goal of providing implementations of time series analysis algorithms often used in astronomy.
Astro Hack Week enabled participants to seed a new collaboration around a software project needed by the larger community, facilitated by the collaborative environment at AHW.
Stingray has since matured into an enduring collaboration within the community with five active maintainers and four Google Summer of Code projects.
\subsubsection*{Example 2: Geo Hack Week}
In 2016, a GHW project team used Google Earth Engine to explore spatial patterns in climate, topography and population data with the goal of mapping the most suitable locations for renewable energy sites in the United States.
The team used machine learning algorithms in conjunction with the powerful hardware resources provided by Google Earth Engine\footnote{\url{http://georgerichardson.net/2017/04/10/searching-for-energy-in-a-random-forest/}}.
%George Richardson, one of the project leads, now works for a renewable resource company in Seattle.
\subsubsection*{Example 3: Neuro Hack Week}
Motion of study participants inside the MRI machine is a major concern in neuroimaging studies.
During NHW 2016, one of the teams focused on a large and openly available data-set of MRI data from children\footnote{ABIDE: \url{http://preprocessed-connectomes-project.org/abide}}.
To test the effect of motion on the results, the team conducted an analysis in which both the number of experimental subjects included, as well as motion cut-off, were varied.
%They tested both the split-half reliability of an analysis of brain connectivity, as well as an analysis that used machine learning to distinguish between brains of children with and without autism spectrum disorder.
The team (composed of four researchers from four different institutions) continued to work on this project remotely after the end of NHW, and eventually published a paper describing these results in the open access journal Research Ideas and Outcomes \cite{leonard2017}.

>>>>

\subsection*{Examples of Hack Week Outcomes}
\label{sec:outcomes}
\subsubsection*{Example 1: Astro Hack Week}
In 2015, a small team used AHW to found a new software project called Stingray\footnote{https://github.com/StingraySoftware/stingray} with the goal of providing implementations of time series analysis algorithms often used in astronomy.
Astro Hack Week enabled participants to seed a new collaboration around a software project needed by the larger community, facilitated by the collaborative environment at AHW.
Stingray has since matured into an enduring collaboration within the community with five active maintainers and four Google Summer of Code projects.
\subsubsection*{Example 2: Geo Hack Week}
In 2016, a GHW project team used Google Earth Engine to explore spatial patterns in climate, topography and population data with the goal of mapping the most suitable locations for renewable energy sites in the United States.
The team used machine learning algorithms in conjunction with the powerful hardware resources provided by Google Earth Engine\footnote{\url{http://georgerichardson.net/2017/04/10/searching-for-energy-in-a-random-forest/}}.
%George Richardson, one of the project leads, now works for a renewable resource company in Seattle.
\subsubsection*{Example 3: Neuro Hack Week}
During NHW 2016, one of the teams analyzed an openly available data-set of MRI data from children\cite{Di_Martino2014-qf}, to test the effects of motion on the results, using varying motion cut-offs.
%They tested both the split-half reliability of an analysis of brain connectivity, as well as an analysis that used machine learning to distinguish between brains of children with and without autism spectrum disorder.
The team (four researchers from  different institutions) continued to work on this project remotely after the end of NHW, and eventually published a paper describing these results \cite{leonard2017}.
